Global Illumination for Fun and Profit

### 2022-02-22 paper.qmd
use a sort-of-compatible plainnat-vgtc bst file

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
documentclass: vgtc
cite-method: natbib
natbiboptions: square, numbers
format:
  pdf:
    template: tvcg.latex
  latex:
    template: tvcg.latex
#  Uncomment the two lines below to also generate an HTML version
#  html:
#    dummy: unused

# Stuff you'll want to change
title: Global Illumination for Fun and Profit
shortauthortitle: "Biv et al.: Global Illumination for Fun and Profit"
author:
  - Roy G. Biv
  - Ed Grimley, *Member, IEEE*
  - Martha Stewart
author-footer:
  - "Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com."
  - "Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com."
  - "Martha Stewart is with Martha Stewart Enterprises at Microsoft Research. E-mail: martha.stewart@marthastewart.com."
abstract: |
  Duis autem vel eum iriure dolor in hendrerit in vulputate
  velit esse molestie consequat, vel illum dolore eu feugiat nulla
  facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
  praesent luptatum zzril delenit augue duis dolore te feugait nulla
  facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
  sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
  aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
  suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
  vel eum iriure dolor in hendrerit in vulputate velit esse molestie
  consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
  accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
  delenit augue duis dolore te feugait nulla facilisi.
bibliography: paper.bib
firstsection: Introduction
keyword:
  - Radiosity
  - global illumination
  - constant time
---

@@

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam
voluptua @Kitware:2003,Max:1995:OMF. At vero eos et accusam et
justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est.

@@

# Quarto Goodies

Just testing the basic stuff.

```{r}
#| echo: false
library(ggplot2)
library(palmerpenguins)
```

```{r}
#| fig-pos: 't'
#| fig-width: 3
#| fig-height: 2
#| echo: false
#| warning: false
#| label: fig-penguins
#| fig-cap: Some penguins, ggplotted.
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) + geom_point()
```

@@

## Acknowledgments {.unnumbered}

(FIXME this unnumbered section should be in small-caps.)

@@

FIXME: Reference font size is too big.

```{=latex}
\bibliographystyle{abbrv-doi}
```

>>>>

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
documentclass: vgtc
cite-method: natbib
natbiboptions: square, numbers
format:
  pdf:
    template: vgtc-quarto-template/tvcg.latex
  # FIXME how does keep_tex work in the yaml?
  latex:
    template: vgtc-quarto-template/tvcg.latex
  #  Uncomment the line below to also generate an HTML version
  html: default

# Stuff you'll want to change
title: Global Illumination for Fun and Profit
shortauthortitle: "Biv et al.: Global Illumination for Fun and Profit"
author:
  - name: Roy G. Biv
    institution: Starbucks Research
    email: "roy.g.biv@aol.com"
  - name: Ed Grimley
    institution: Grimley Widgets, Inc.
    email: "ed.grimley@aol.com"
  - name: Martha Stewart
    institution: Martha Stewart Enterprises at Microsoft Research
    email: "martha.stewart@marthastewart.com"

# If you are submitting a paper to a conference for review with a double
# blind reviewing process, please uncomment the line below and use your
# OnlineID. 
# online-id: 987654321

# please declare the paper type of your paper to help reviewers, only shown in review mode
# choices:
#   algorithm/technique
#   application/design study
#   evaluation
#   system
#   theory/model
paper-type: please specify

abstract: |
  Duis autem vel eum iriure dolor in hendrerit in vulputate
  velit esse molestie consequat, vel illum dolore eu feugiat nulla
  facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
  praesent luptatum zzril delenit augue duis dolore te feugait nulla
  facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
  sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
  aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
  suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
  vel eum iriure dolor in hendrerit in vulputate velit esse molestie
  consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
  accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
  delenit augue duis dolore te feugait nulla facilisi.
bibliography: paper.bib
firstsection: Introduction
keyword:
  - Radiosity
  - global illumination
  - constant time
---

@@

TBF.

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam
voluptua [@Kitware:2003,Max:1995:OMF]. At vero eos et accusam et
justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est.

@@

# Quarto Features

## Citation styles

Defend a claim by referencing a paper [@Isenberg:2017:VMC].

As @Kindlmann:1999:SAG has shown, it is possible to generate transfer functions semi-automatically.

## Computational Output

```{r}
#| echo: false

# this won't be printed to the paper at all, since it produces no
# output.
library(ggplot2)
library(palmerpenguins)
```

```{r}
#| fig-pos: 't'
#| fig-width: 3
#| fig-height: 2
#| echo: false
#| warning: false
#| label: fig-penguins
#| fig-cap: Some penguins, ggplotted.

# the source code won't be printed to the paper, but the output will.
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) + geom_point()
```

<!--- this also works for Python --->
```{python}
import math
print(math.sqrt(2))
```

@@

# Acknowledgments {.unnumbered}

@@
